Seismic Hazard Estimation of Northern Iran Using Smoothed Seismicity

### 2016-10-21 response.tex

\clubpenalty=10000  % Orphan - First of paragraph left behind
\widowpenalty=10000 % Widow  - Last of paragraph sent ahead

\setallmargins{1in}

\begin{document}

% ******************************************************************
% *************************** REVIEWER 1 ***************************
% ******************************************************************

@@

\begin{center}
	\bf
	\large
	Authors' Response to Reviewer 1
\end{center}

\noindent
We thank the reviewer for his/her comments and suggestions, which helped us improve the manuscript. To help the review process, in the annotated manuscript version of the paper, we have highlighted the most relevant changes that resulted from these comments in green font. In the following, we provide a response to each comment. The original comments are in italic black font, followed by our responses in regular blue font.
\vspace{2ex}
\newline

@@

\introcomment{~}{%
The authors perform a seismic hazard analysis for northern Iran using a newly developed source model from smoothed seismicity. The work is an important contribution to seismic hazard analyses in Iran. Development of the seismic source model follows a careful analysis of the earthquake catalogs for information about spatially varying earthquake rates, maximum magnitudes and b-values. The authors are careful to acknowledge that alternative means for estimating earthquake recurrence - and for other components of the source and ground motion characterization - also exist, and that this work is only one approach for characterizing hazard in the region.
}

\comment{1}{%
Page 3, Line 71: A short, summary description of previous source models would highlight the contribution of this work. In particular, summary details of the work by Khodaverdian et al should be included to indicate how the approach of the authors differs from previous work.
}

\response{%
We modified parts of the introduction as well as other sections to highlight in a more explicit manner the differences in our study with respect to other previous efforts. In the case of Khodaverdian et al (2016), the major difference is in the way the seismicity parameters $b$ and $M_{\max}$ are calculated. This is mentioned in the Introduction, and addressed with more clarity in Section 4 (page 11, line 312) and in Section (page 17, line 495). As mentioned there, the difference resides in the fact that Khodaverdian et al (2016) compute seismic parameters for grid cells of size 1\textdegree{} $\times$ 1\textdegree{}. This means the they compile earthquake catalogs for each grid point considering events within 200 km radius from the grid point, whereas we assume the seismic parameters to be uniform for each tectonic seismic region.
}

\comment{2}{%
Page 3, line 77: Fault-based/geologic-based earthquake recurrence estimates
}

\response{%
Added, thanks.
}

\comment{3}{%
Page 4, line 106: Should this be northwest?
}

\response{%
Yes. Fixed.
}

\comment{4}{%
Page 6, line 168: It would be good to add a reference for the GEM effort.
}

\response{%
We do not have a direct reference to GEM but added a citation to Zare et al (2014), where the connection to GEM is mentioned explicitly.
}

\comment{5}{%
Pages 7--8: Discussion about identifying the completeness level of the earthquake catalogs is a bit confusing. Typically, one either specifies a minimum magnitude of completeness ($M_c$) and then tries to identify the earliest time for which events or complete; or, one specifies a year and computes the corresponding $M_c$. In reading the text, it appears that both methods were used. Please clarify.
}

\response{%
The new version of the Completeness sub-section now clarifies this point. The reviewer is right in that we used both methods, but we originally did not clearly explain the procedure. We first compute the $b$ and $M_{\max}$ values for each region, or the uniform model, using the HA3 package written by Dr.~Kijko. At this point, $M_c$ is used as an input to the HA3 software. We then used the Seiskit package written by Dr.~Frankel to compute the smoothed seismicity $a$-values. At this point, SeisKit uses the start year of completeness for each magnitude range. Please see changes in page 8, lines 211 and 229.
}

\comment{6}{%
Pages 7--8: The authors should note that some authors use an alternative smoothing kernel $(~exp(-(D/2*sigma)^2)$. Comparison of the smoothing length between different studies may require consideration of a $sqrt(2)$ factor.
}

\response{%
We added a note to this effect in Section 4, and cite the work of Moschetti (2015) as an example. A complete analysis of the smoothing length and its influence on the hazard analysis, however, is out of the scope of the present study. The modifications done can be found in page 10, line 295.
}

\comment{7}{%
Page 7--8: In addition to the Mirzaei et al (1997) reference, some authors employ likelihood testing of smoothed seismicity rate models to identify optimal smoothing lengths for adaptive and fixed smoothed seismicity methods (e.g., Werner et al., 2011; Moschetti, 2015).
}

\response{%
We included a note to reflect this and added the references suggested by the reviewer. The changes can be seen in page 11, line 304.
}

\comment{7}{%
Page 9: Kagan and Jackson (1994) should also be included in the reference list.
}

\response{%
We added the suggested reference to the list provided in page 10, line 278.
}

\comment{8}{%
Page 10, line 302: ``...subjective decisions and any reasonable choice...'' I would disagree that these are subjective decisions. My opinion is that you have applied scientific judgment. You clearly need to communicate where judgment is applied; however:
\\[5pt]
Details about the implementation of the two seismicity rate models (U, R) should be expanded. Are sub-catalogs developed for the five separate regions and then used to develop separate a-grids? Presumably, the separate rate files are then used to compute hazard curves and are summed at each location.
\\[5pt]
A logic tree would be of great benefit in clarifying how the source models are combined. In particular, it would clarify the weighting from different completeness levels.
\\[5pt]
Plots of seismicity rates from the R and U models would be of interest and particularly relevant given that the smoothed seismicity model is the main contribution of this work to hazard analyses for Iran.
}

\response{%
The reviewer was right to suggest that our original approach to present a combination of the R and U models was not the best. In the revised manuscript we have addressed this in two basic manners. First, we now provide a better explanation of the rationale behind both models and the reasons to provide a combined result. Second, we adopted the suggestion of implementing a logic tree approach in our analysis. The adopted logic tree allows us to consider the epistemic uncertainty in the defintion of the seismic zones and also allowed us to include uncertainties in the seismic parameters $b$ and $M_{\max}$. For each branch of the logic tree we assigned weights following literature recommendations and our own judgement. In total, traversing and combining the different branches meant to conduct 162 runs ( $3 M_{\max} \times 3 b \times (5 \mbox{regions} + 1 \mbox{uniform}) \times 3 \mbox{GMPE}$) to get the combined results of the 2 basic models (R and U), three values of $b$ and $M_{\max}$ and three GMPE alternatives. The associated changes can be seen in various sections of the revised manuscript, and in particular in the new Section 7 and the Results Section 8.
}

\comment{9}{%
Page 14, line 391: The incorporation of smaller earthquakes $(M<5)$ will have a significant influence on the hazard associated with PGA. Recent papers by Atkinson and others have demonstrated this effect. You may wish to argue that $M_{\min}$ was chosen based on the expected smallest magnitude capable of causing damage.
}

\response{%
We revised the computations and now present results for events with $M_w > 4.5$. The text was modified accordingly (see page 4, line 94).
}

\comment{10}{%
Figure 7: Is the magnitude-frequency distribution just a truncated ($M_{\min}$, $M_{\max}$) Gutenberg-Richter model? Figure 7 suggests that the MFD may be tapered?
}

\response{%
Yes, it is truncated Gutenberg-Richter model. We now make this explicit in the caption of the figure.
}

\comment{11}{%
Page 12, line 345: ``...controls the spatial extent to which the local occurrence of earthquakes...'' I would argue that the smoothed seismicity controls the local occurrence and spatial distribution of earthquakes and that the GMPEs control the intensity level at a particular site given earthquake locations and magnitudes from your source model.
}

\response{%
That is correct. We have modified this sentence accordingly. Please se changes in page 13, line 365.
}

\comment{12}{%
Page 13, line 361: Change ``approached'' to ``approach'' and ``lead'' to ``led.''
}

\response{%
This part of the text was modified and the requested change may no longer apply, at least in regard to the first suggestion. Regarding the second suggestion, we do not quite agree. Although there was a typo, the way the sentence was structured, the corrected version uses ``leads'' instead.
}

\comment{13}{%
The approach to generating Figure 10 should be clarified. It appears that the probabilistic ground motions from the R and U model are averaged and used to compute a standard deviation. The formal method for combining alternative models in PSHA is through the logic tree; this is equivalent to weighting the models in hazard (rate) space, rather than in ground motion (intensity, PGA) space. It appears that the authors have done the latter, though I may be incorrect. If this is the case, please correct. It is very reasonable to combine the R and U models to produce another alternative model. This work is not a comprehensive seismic hazard analysis, and presentation of probabilistic ground motions from the R, U and a weighted model would be reasonable goal. However, I would caution against comparing probabilistic ground motion maps with maps of seismicity because the varying $b$- and $M_{\max}$-values for the R model greatly complicate the comparison. As mentioned earlier, formal testing methods exist for ensuring consistency of observed earthquake locations with the smoothed seismicity models (see CSEP references, Zechar, Schorlemmer, Werner, Helmstetter, Jackson; Moschetti, 2015). Applying these methods is beyond the scope of this work, but might be recognized as a future direction.
}

\response{%
Thanks for the informative comment. In the original figure 10 we combined the regional (R) and uniform (U) results (i.e., we combined the probabilities of exceedance, and then computed the PGA) with similar weights (i.e., 0.5). The positive and negative standard deviation plots came from GMPE + Uncertainty and GMPE -- Uncertainty. Our original intention was to show the range of variation for PGA around the median value. However, in the revised version of the manuscript this is no longer done. The new figure corresponding to the (R,U) combined model (Fig.~12) is now the result of the complete logic tree analysis, which is a more appropriate approach to presenting the results of our analysis.
}

% ******************************************************************
% *************************** REVIEWER 2 ***************************
% ******************************************************************

### 2016-10-21 abstract.tex
some final changes

%
This article presents a seismic hazard assessment for northern Iran, where a smoothed seismicity approach has been used in combination with an updated seismic catalog and a ground motion prediction equation recently found to yield good fit with data. We evaluate the hazard over a geographical area including the seismic zones of Azerbaijan, the Alborz Mountain Range, and Kopeh-Dagh, \myrevision{and parts of other neighboring seismic zones that fall within our region of interest. In the chosen approach, seismic events are not assigned to specific faults but assumed to be potential seismogenic sources distributed within regular grid cells. After performing the corresponding magnitude conversions, we decluster both historical and instrumental seismicity catalogs to obtain earthquake rates based on the number of events within each cell, and smooth the results to account for the uncertainty in the spatial distribution of future earthquakes. Seismicity parameters are computed for each seismic zone separately, and for the entire region of interest as a single uniform seismotectonic region. In the analysis we consider uncertainties in the ground motion prediction equation, the seismic parameters and combine the resulting models using a logic tree.} The results are presented in terms of expected peak ground acceleration (PGA) maps and hazard curves at selected locations, considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions. \myrevision{According to our results, the highest levels of hazard are observed west of the North Tabriz and east of the North Alborz faults, where expected PGA values are between about 0.5 g and 1 g for 10 and 2 percent probability of exceedance in 50 years, respectively.} We analyze our results in light of similar estimates available in the literature and offer our perspective on the differences observed. We find our results to be helpful in understanding seismic hazard for northern Iran, \myrevision{but recognize that additional efforts are necessary to obtain more robust estimates at specific areas of interest and different site conditions}.

>>>>

%
This article presents a seismic hazard assessment for northern Iran, where a smoothed seismicity approach has been used in combination with an updated seismic catalog and a ground motion prediction equation recently found to yield good fit with data. We evaluate the hazard over a geographical area including the seismic zones of Azerbaijan, the Alborz Mountain Range, and Kopeh-Dagh, \myrevision{and parts of other neighboring seismic zones that fall within our region of interest. In the chosen approach, seismic events are not assigned to specific faults but assumed to be potential seismogenic sources distributed within regular grid cells. After performing the corresponding magnitude conversions, we decluster both historical and instrumental seismicity catalogs to obtain earthquake rates based on the number of events within each cell, and smooth the results to account for the uncertainty in the spatial distribution of future earthquakes. Seismicity parameters are computed for each seismic zone separately, and for the entire region of interest as a single uniform seismotectonic region. In the analysis we consider uncertainties in the ground motion prediction equation, the seismicity parameters and combine the resulting models using a logic tree.} The results are presented in terms of expected peak ground acceleration (PGA) maps and hazard curves at selected locations, considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions. \myrevision{According to our results, the highest levels of hazard are observed west of the North Tabriz and east of the North Alborz faults, where expected PGA values are between about 0.5 g and 1 g for 10 and 2 percent probability of exceedance in 50 years, respectively.} We analyze our results in light of similar estimates available in the literature and offer our perspective on the differences observed. We find our results to be helpful in understanding seismic hazard for northern Iran, \myrevision{but recognize that additional efforts are necessary to obtain more robust estimates at specific areas of interest and different site conditions}.

### 2016-10-21 compilation.tex
almost done with section 8
some final changes

\begin{figure*}[t]
	\centering
	\includegraphics[width=0.9\textwidth]{figures/pdf/figure-03}
	\caption{Location of events considered in the compiled seismic catalog \myrevision{for the complete region of interest}. (a) Historical seismicity prior to 1900 for $M_w \geq 4$ \citep[after][]{Zare2014}. (b) Instrumental seismicity up until December 2015 for $M_w \geq 3$ (IIEES) and $M_w \geq 4$ \citep[after][]{Zare2014}. Size of symbols is proportional to the magnitude of the events. In the case of the historical seismicity catalog, the color fill indicates the year of the event. The borderlines of the seismic zones shown in Fig.~\ref{fig:iran} are shown in the background in white, along with the light gray shaded relief \myrevision{in the background. The dashed box indicates the effective region of interest}.}
	\label{fig:catalog}
\end{figure*}

@@

\begin{figure*} [t]
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-04}
	\caption{Magnitude-time distribution of earthquakes in each of the seismic zones, and the complete region of interests (here referred to as the uniform model).}
	\label{fig:scatter}
\end{figure*}

>>>>

\begin{figure*}[t]
	\centering
	\includegraphics[width=0.9\textwidth]{figures/pdf/figure-03}
	\caption{Location of events considered in the compiled seismic catalog \myrevision{for the complete region of interest}. (a) Historical seismicity prior to 1900 for $M_w \geq 4$ \citep[after][]{Zare2014}. (b) Instrumental seismicity up until December 2015 for $M_w \geq 3$ (IIEES) and $M_w \geq 4$ \citep[after][]{Zare2014}. Size of symbols is proportional to the magnitude of the events. In the case of the historical seismicity catalog, the color fill indicates the year of the event. The borders of the seismic zones shown in Fig.~\ref{fig:iran} are shown in the background in thin white lines, along with the light-gray shaded relief \myrevision{in the background. The dashed box indicates the effective region of interest}.}
	\label{fig:catalog}
\end{figure*}

\begin{figure*}[t]
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-04}
	\caption{Magnitude-time distribution of earthquakes in each of the seismic zones, and the complete region of interests (here referred to as the uniform model).}
	\label{fig:scatter}
\end{figure*}

@@

### 2016-10-21 conclusions.tex
some final changes

We present results from a seismic hazard analysis for northern Iran based on a smoothed seismicity approach, including regional maps of expected peak ground accelerations for different seismic zonation models. In particular, we calculated the hazard for the region of interest using two basic models, a five-seismic zone regions model and a uniform seismic zone model, \myrevision{including uncertainty in the combination of both models, the seismic parameters, and the selection of a ground motion prediction equation via a logic tree approach. In general, our calculations yield results similar to those of other studies for the region of interest and the main cities in it. We, however, provide a more complete perspective to the problem of seismic hazard analysis for norther Iran than previous studies because our use of a more complete seismic catalog, which includes recent damaging events and low-magnitude earthquakes. In our analysis we found that the combination of the regional and uniform models not only allowed us to account for the uncertainty in seismic zonation but it led to a final hazard map that adjusted better to the visual interpretation of the historical and instrumental seismicity observed in the region of interest, the location of known seismically active faults, and the low-magnitude seismic activity in the region}. While no one model can be deemed more appropriate than others, we believe our results constitute a positive contribution to the understanding of seismic hazard in the region, especially for rural areas that are not the subject of specialized hazard studies such as those conducted for major urban centers. Future work to improve the results presented here should consider \myrevision{other ground motion measures of intensity} such as response spectral accelerations for different periods and site effects.

>>>>

We present results from a seismic hazard analysis for northern Iran based on a smoothed seismicity approach, including regional maps of expected peak ground accelerations for different seismic zonation models. In particular, we calculated the hazard for the region of interest using two basic models, a five-seismic zone regions model and a uniform seismic zone model, \myrevision{including uncertainty in the combination of both models, the seismic parameters, and the selection of a ground motion prediction equation via a logic tree approach. In general, our calculations yield results similar to those of other studies for the region of interest and the main cities in it. We, however, provide a newer and alternative perspective to the problem of seismic hazard analysis for norther Iran than previous studies because our use of a more complete seismic catalog, which includes recent damaging events and low-magnitude earthquakes. In our analysis we found that the combination of the regional and uniform models not only allowed us to account for the uncertainty in seismic zonation but it led to a final hazard map that adjusted better to the visual interpretation of the historical and instrumental seismicity observed in the region of interest, the location of known seismically active faults, and the low-magnitude seismic activity in the region}. While no one model can be deemed more appropriate than others, we believe our results constitute a positive contribution to the understanding of seismic hazard in the region, especially for rural areas that are not the subject of specialized hazard studies such as those conducted for major urban centers. Future work to improve the results presented here should consider \myrevision{other ground motion measures of intensity} such as response spectral accelerations for different periods and site effects.

### 2016-10-21 logictree.tex
some final changes

\myrevision{As mentioned in previous sections, we address the uncertainties in our models, seismic parameters and selected ground motion prediction equation via a logic tree. Fig.~\ref{fig:logic} shows the complete set of branches at each of the tree nodes. In particular, we consider uncertainty in the seismic zonation via the combination of the R and U models, the maximum magnitude $M_{\max}$, the seismic $b$-value, and the prediction of PGA intensities in the GMPE by \citet{Kalkan2004}. We assigned the weights to the R and U model arbitrarily, giving more weight to the regional model R based on the expectation that a regionalized model would likely lead to a better seismic hazard analysis. The uncertainty in $M_{\max}$ and the $b$ values were set equal to the plus and minus ranges shown in Table \ref{tab:params}. Finally, the uncertainty in the GMPE---that is, the upper and lower bounds taken as alternative GMPEs---was based on the amplitude of one standard deviation, $\sigma_{\ln y} = 0.612$. The weights assigned in the logic tree to these additional sources of uncertainty were defined based on previous studies \citep[e.g.,][]{Petersen2015}.}

>>>>

\myrevision{As mentioned in previous sections, we address the uncertainties in our models, seismic parameters and selected ground motion prediction equation via a logic tree. Fig.~\ref{fig:logic} shows the complete set of branches at each of the tree nodes. In particular, we consider uncertainty in the seismic zonation via the combination of the R and U models, the maximum magnitude $M_{\max}$, the seismic $b$-value, and the prediction of PGA intensities in the GMPE by \citet{Kalkan2004}. We assigned the weights to the R and U model arbitrarily, giving more weight to the regional model R based on the expectation that a regionalized model would likely lead to a better seismic hazard analysis. The uncertainty in $M_{\max}$ and the $b$ values were set equal to the plus and minus ranges shown in Table \ref{tab:params}. Finally, the uncertainty in the GMPE---that is, the upper and lower bounds taken as alternative GMPEs---was based on the amplitude of one standard deviation, $\sigma_{\ln y} = 0.612$. The weights assigned in the logic tree to these additional sources of uncertainty were defined based on previous studies \citep[e.g.,][]{Petersen2008}.}

### 2016-10-21 parameters.tex
up to logic tree
almost done with section 8
some final changes

@@

\myrevision{
\begin{table}%[t]
    \centering
    \caption{Seismicity parameters $b$ and $M_{\max}$ computed for the seismic zones in our region of interest and the reference uniform seismicity model along with the observed maximum magnitude, $M_{\max}^{\mathrm{obs}}$.}
    \begin{tabular}{@{\hspace{0.2ex}}lccc@{\hspace{0.2ex}}}
        \cline{2-4}                                                                         \\[-1.6ex]
                        & $b$-value         & $M_{\max}$        & $M_{\max}^{\mathrm{obs}}$ \\[0.6ex]
        \hline                                                                              \\[-1.6ex]
        Azerbaijan      & 1.15 $\pm$ 0.03   & 7.80 $\pm$ 0.50   & 7.7                       \\
        Alborz          & 0.97 $\pm$ 0.02   & 7.82 $\pm$ 0.52   & 7.8                       \\
        Kopeh Dagh      & 0.93 $\pm$ 0.03   & 7.74 $\pm$ 0.29   & 7.6                       \\
        Zagros          & 1.05 $\pm$ 0.02   & 7.48 $\pm$ 0.26   & 7.4                       \\
        Central-East    & 0.99 $\pm$ 0.02   & 7.80 $\pm$ 0.37   & 7.6                       \\
        Uniform Model   & 0.98 $\pm$ 0.01   & 7.80 $\pm$ 0.28   & 7.8                       \\[0.5ex]
        \hline
    \end{tabular}
    \label{tab:params}
\end{table}
}

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/pdf/figure-07}
    \caption{Annual probability of exceedance as a function of earthquake magnitude for the seismic zones in the region of interest. The three curves in red correspond to those seismic zones completely considered within the study area, whereas the ones in blue are the two additional contributing zones from the rest of the country. The last curve in green corresponds to the complete region of interest, here referred to as the uniform model. The shaded range indicates the models' $\pm 1$ standard deviation.}
    \label{fig:annualp}
\end{figure*}

>>>>

\begin{table}%[t]
    \centering
    \caption{Seismicity parameters $b$ and $M_{\max}$ computed for the seismic zones in our region of interest and the reference uniform seismicity model along with the observed maximum magnitude, $M_{\max}^{\mathrm{obs}}$.}
    \myrevision{
    \begin{tabular}{@{\hspace{0.2ex}}lccc@{\hspace{0.2ex}}}
        \cline{2-4}                                                                         \\[-1.6ex]
                        & $b$-value         & $M_{\max}$        & $M_{\max}^{\mathrm{obs}}$ \\[0.6ex]
        \hline                                                                              \\[-1.6ex]
        Azerbaijan      & 1.15 $\pm$ 0.03   & 7.80 $\pm$ 0.50   & 7.7                       \\
        Alborz          & 0.97 $\pm$ 0.02   & 7.82 $\pm$ 0.52   & 7.8                       \\
        Kopeh Dagh      & 0.93 $\pm$ 0.03   & 7.74 $\pm$ 0.29   & 7.6                       \\
        Zagros          & 1.05 $\pm$ 0.02   & 7.48 $\pm$ 0.26   & 7.4                       \\
        Central-East    & 0.99 $\pm$ 0.02   & 7.80 $\pm$ 0.37   & 7.6                       \\
        Uniform Model   & 0.98 $\pm$ 0.01   & 7.80 $\pm$ 0.28   & 7.8                       \\[0.5ex]
        \hline
    \end{tabular}
    }
    \label{tab:params}
\end{table}

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/pdf/figure-07}
    \caption{Annual probability of exceedance as a function of earthquake magnitude for the seismic zones in the region of interest \myrevision{following a truncated Gutenberg-Richter model}. The three curves in red correspond to those seismic zones completely considered within the study area, whereas the ones in blue are the two additional contributing zones from the rest of the country. The last curve in green corresponds to the complete region of interest, here referred to as the uniform model. The shaded range indicates the models' $\pm 1$ standard deviation.}
    \label{fig:annualp}
\end{figure*}

@@

### 2016-10-21 results.tex
some final changes

\myrevision{We also note that the overall distribution of mean PGA agrees with the recent study by \citet{Khodaverdian_2016_BSSA}. However, their results are in general slightly lower than ours. Obviously, given the differences in the catalogs, completeness magnitude, and in the seismicity parameters $M_{\max}$ and $b$, we cannot expect PGA values to match. For example, in the case of the $b$ values, \citet{Khodaverdian_2016_BSSA} reported large variations netween 0.56 and 1.27, where over 50 percent of the grid points had $b$ values greater than 1; whereas in our study the $b$ values observe a narrow range of variation between 0.93 and 1.15. In this regard we should note that \citet{Khodaverdian_2016_BSSA} computed the seismicity parameters for each grid point considering the contributions within a circular area of radius 200 m, whereas we considered a uniform seismicity parameters for each region and account for the uncertainty in the difference between regions via the combination of the R and U models.}

\myrevision{Altogether, on average, we found our results to be in good agreement with other previous results. For the city of Uremia, for instance, we obtained a expected PGA of 0.24 g, which is slightly lower than values obtained by \citet{BHRC2014} and \citet{Zare2012} and higher than \citet{Khodaverdian_2016_BSSA} for a 10 percent probability of exceedance in 50 years. We believe \citet{Zare2012} obtained higher values because their of use of a parametric method. For a 2 percent probability of exceedance in 50 years, \citet{Golara2014} obtained expected PGAs on the order of 0.3--0.5 g, where our mean value is 0.38 g. For the city of Tabriz, our results match with those obtained by \citet{BHRC2014} and are within the range of values computed by \citet{Zare2012}, for a 10 percent probability. These and other similar comparisons are summarized in Table \ref{tab:pga}, where we show our results and those of other previous studies for selected cities in northern Iran.}

>>>>

\myrevision{We also note that the overall distribution of mean PGA agrees with the recent study by \citet{Khodaverdian_2016_BSSA}. However, their results are in general slightly lower than ours. Obviously, given the differences in the catalogs, completeness magnitude, and in the seismicity parameters $M_{\max}$ and $b$, we cannot expect PGA values to match. For example, in the case of the $b$ values, \citet{Khodaverdian_2016_BSSA} reported large variations between 0.56 and 1.27, where over 50 percent of the grid points had $b$ values greater than 1; whereas in our study the $b$ values observe a narrow range of variation between 0.93 and 1.15. In this regard we should note that \citet{Khodaverdian_2016_BSSA} computed the seismicity parameters for each grid point considering the contributions within a circular area of radius 200 m, whereas we considered a uniform seismicity parameters for each region and account for the uncertainty in the difference between regions via the combination of the R and U models.}

\myrevision{Altogether, on average, we found our results to be in good agreement with other previous results. For the city of Urmia, for instance, we obtained a expected PGA of 0.24 g, which is slightly lower than values obtained by \citet{BHRC2014} and \citet{Zare2012} and higher than \citet{Khodaverdian_2016_BSSA} for a 10 percent probability of exceedance in 50 years. We believe \citet{Zare2012} obtained higher values because their of use of a parametric method. For a 2 percent probability of exceedance in 50 years, \citet{Golara2014} obtained expected PGAs on the order of 0.3--0.5 g, where our mean value is 0.38 g. For the city of Tabriz, our results match with those obtained by \citet{BHRC2014} and are within the range of values computed by \citet{Zare2012}, for a 10 percent probability. These and other similar comparisons are summarized in Table \ref{tab:pga}, where we show our results and those of other previous studies for selected cities in northern Iran.}
